Synthesising and Verifying Closed-loop Digital Control Systems

### 2016-09-19 paper/paper.tex
add preliminaries

\title{TBD}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example}

@@

The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $P(z)$. However, if implementation aspects are considered during verification, this controller becomes unstable. To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format 
\param{k}{l} ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).

>>>>

\title{Synthesising and Verifying Closed-loop Digital Control Systems}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries}

%------------------------------------
\subsection{Verifying Closed-loop Control Systems}
\label{verifying-closed-loop-control-systems}
%------------------------------------

In this study, the methodology used for verifying closed-loop digital control system is based on the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control systems considering finite-word length (FWL) effects in the digital controller and uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}. Let $C(z)$ be a digital controller and $P(z)$ be a plant model given as

\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
P(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}

\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$ and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits of the integer and fractional part, respectively. Note that $P(z)$ is a discrete model of a real (and continuous) plant, {\it i.e.}, a continuous model of the plant must be discretized to obtain the discrete equivalent coefficients $b$ and $a$~\cite{Astrom08}. Although there are several discretization methods available in the literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is more suitable for representing the sampling processes that are typically employed by hybrid systems~\cite{istepanian2012digital}.

Let $C(z)$ and $P(z)$ transfer functions be arranged in vectors $c_0$ and $p_0$, respectively.
For each $C(z)$ implementation, there is a function $FWL[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format \param{N_C}{_C}. The quantized controller parameters vector ($c$) is generated via $FWL[c_0]$. The uncertain plant parameters ($p$) can be expressed as

\begin{equation}
p = p_0 + \Delta{p} = \left [
				\begin{tabular}{c}
				$b_{0}+\Delta{b_{0}} ~ b_{1}+\Delta{b_{1}} ~ ... ~ b_{M_G}+\Delta{b_{M_G}}$ \\%~ 
				$a_{0}+\Delta{a_{0}} ~ a_{1}+\Delta{a_{1}} ~ ... ~ a_{N_G}+\Delta{a_{N_G}}$
				\end{tabular}
				\right ],
\end{equation}

\vspace{1 mm} 
\noindent where $\Delta{p}$ represents the plant uncertainties coefficients. The polynomial set of possible values of $p$ is denoted by $\mathfrak{P}$.

%------------------------------------
\subsection{DSVerifier Verification Flow}
\label{verification-flow}
%------------------------------------

DSVerifier verification flow is shown in Fig.~\ref{DSVerifier_process}. Steps from $1$ to $5$ are performed by users and Steps A to D are automatically performed by DSVerifier, which accepts the digital controller transfer functions together with the plant model. For any digital controller, implementation details should be provided ({\it e.g.}, number of bits, realization, and sample time).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.pdf}
\caption{DSVerifier Verification Flow.}
\label{DSVerifier_process}
\end{figure*}

In Step $1$, the user provides inputs $p_0$ and $\Delta{p}\%$ ({\it i.e.}, percentage form of $\Delta{p}$), which contain the plant model and the interval, respectively. In Step $2$, a digital controller must be designed with any preferred method, where $c_0$ is obtained. The controller numerical representation and realization form are chosen in Steps $3$ and $4$, respectively. In Step $5$, the user finally configures the verification parameters ({\it e.g.}, verification time, properties, and BMC tool). After that, DSVerifier verification engine performs an (automatic) verification of the desired property $\phi$ ({\it i.e.}, stability). The user steps described in Steps $1$-$5$ results in an ANSI-C code that should be used as an input for DSVerifier.

In Step A, DSVerifier constructs a non-deterministic model to represent the plant family $\mathfrak{P}$ using $p_0$ and $\Delta{p}\%$, which are provided in Step $1$. DSVerifier then formulates $FWL[\cdot]$ in Step B using implementation details provided from Steps $2$ and $3$, and then computes $FWL[c_0]$ in Step C. Thus, DSVerifier builds an intermediate ANSI-C code for the digital system implementation, which is used as input for the model-checker, as pointed in Step D.

This intermediate ANSI-C code model has three main modules: digital controller code to be embedded into the microprocessor; plant model code, which simulates the plant model dynamics considering uncertainties; and ``assert'' and ``assume'' statements, which control the verification flow. For the digital controller code, transfer functions coefficients are quantized and deterministic, and all operations use fixed-point arithmetic. In the plant model code, transfer function coefficients are not quantized, but represented with maximum precision based on double data-type variables; they are treated as non-deterministic variables to support model uncertainties. The directive ``assume'' bounds non-deterministic variables, {\it i.e.}, inputs and plant uncertain coefficients.

Finally in the Step D, the translation of ANSI-C code into SAT/SMT formulae is done by a back-end model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}). Here, DSVerifier symbolically checks a given property $\phi$ with respect to closed-loop systems, which are composed by $FWL[c_0]$ and every $p$ in $\mathfrak{P}$. If any property violation is found, then DSVerifier reports a counterexample, which contains system inputs or parametric deviations $\Delta{p}\%$ that lead the system to a failure. A successful verification result is reported if the system is safe with respect to $\phi$. In particular, the stability verification is complete and sound, since it does not depend on system outputs and inputs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example}

@@

The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $P(z)$. However, if implementation aspects are considered during verification, this controller becomes unstable.
